### 2023-01-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@802ef7496e248930957db84934b8e3bb47c66fe6 🚀

        {\bfseries 1:}\,Community ecologists are increasingly shifting
from a binary thinking of food webs and other ecological networks (e.g.,
do species interact?) to a more probabilistic perspective (e.g., how
likely are species to interact?). Assuredly, the benefits of
representing ecological interactions as probabilistic events are
numerous, from a better assessment of the spatial variation of trophic
interactions to an increase capacity to reconstruct networks from sparse
data.\\%
        {\bfseries 2:}\,However, probabilities need to be used with
caution when working with species interactions. Indeed, depending on the
system at hand and the method used to build probabilistic networks,
probabilities can have different interpretations that imply different
ways to manipulate them. This is rarely discussed in the literature,
thus impeding our ability to use data on probabilistic interactions
appropriately.\\%
        {\bfseries 3:}\,At the core of these differences lie the
distinction between assessing the likelihood that two groups of
individuals \emph{can} interact and the likelihood that they \emph{will}
interact. This impacts the spatial, temporal, and taxonomic scaling of
interaction probabilities, thus further enlightening the need to
properly define them in their ecological context.\\%
        {\bfseries 4:}\,With these challenges in mind, we propose a
general approach to thinking about probabilities in regards to
ecological interactions, with a strong focus on food webs, and call for
better definitions and conceptualizations of probabilistic ecological
networks, both at the local and regional scales.\\%

>>>>

        {\bfseries 1:}\,Community ecologists are increasingly thinking
probabilistically when it comes to food webs and other ecological
networks. Assuredly, the benefits of representing ecological
interactions as probabilistic events (e.g., how likely are species to
interact?) instead of binary objects (e.g., do species interact?) are
numerous, from a better assessment of the spatiotemporal variation of
trophic interactions to an increase capacity to reconstruct networks
from sparse data. However, probabilities need to be used with caution
when working with species interactions. Indeed, depending on the system
at hand and the method used to build probabilistic networks,
probabilities can have different interpretations that imply different
ways to manipulate them. At the core of these differences lie the
distinction between assessing the likelihood that two groups of
individuals \emph{can} interact and the likelihood that they \emph{will}
interact. This impacts the spatial, temporal, and taxonomic scaling of
interaction probabilities, thus enlightening the need to properly define
them in their ecological context. Published data on probabilistic
species interactions are poorly documented in the literature, which
impedes our ability to use them appropriately. With these challenges in
mind, we propose a general approach to thinking about probabilities in
regards to ecological interactions, with a strong focus on food webs,
and call for better definitions and conceptualizations of probabilistic
ecological networks, both at the local and regional scales.\\%
